Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-03-13 docs/ms.tex
Update ms.tex

\subsection{Posterior samples}
We show the posterior samples of both g and $\alpha$ ,for both beta function and step function model.
\subsection{Bias Test}
We test the systematical bias of our estimator.
We plot $g_{1}-g_{1}^{true}$ VS $g_{1}^{true}$ ,and put on an error bar which equals standard deviation of 
marginalized likehood functon $p(Data|g_{1})$ ,and use a linear fit to determin the m,c value and their standard 
deviations.

@@

\subsection{Accuracy Test}
We show some example how our method works when there is an Gaussian noise added on the observed $\epsilon$

>>>>

\subsection{Posterior samples}
We show the posterior samples of both g and $\alpha$ ,for both beta function and step function model.
\subsection{Bias Test}
We test the systematical bias of our estimator.(Here the estimator is the max-marginalized likelihood estimator?)
We plot $g_{1}-g_{1}^{true}$ VS $g_{1}^{true}$ ,and put on an error bar which equals standard deviation of 
marginalized likehood functon $p(Data|g_{1})$ ,and use a linear fit to determin the m,c value and their standard 
deviations.

@@

\subsection{Measurement Error}
We show some example how our method works when there is an Gaussian noise added on the observed $\epsilon$
